Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-07-28 paper-v1.tex
Bold for figure numbers in caption/text. @naszam

\begin{figure}
\centering
\includegraphics[scale=0.28]{AntsReview}
\caption{Exagones represent the protocol's smart contracts. Ellipse represents the smart contract inherited by AntsReview. Clouds represent integrations into the protocol. Rectangles represent smart contracts' libraries.
\textbf{a)} Core contract of the protocol implementing a bounty system with the functions listed.
\textbf{b)} Module inherited by AntsReview: it manages the access control of the protocol by adding and removing issuers and peer-reviewers.
\textbf{c)} Native token used in the protocol that inherits the \textbf{d)} contract from \emph{OpenZeppelin}. It is linked to \textbf{a)} and to \textbf{e)}, wrapped into \emph{zkANTS} to implement private \emph{ANTS} transactions on Ethereum.
\textbf{f)} Integration with IPFS to upload papers, requirements and peer-reviews and store the hash as \emph{PoE} into AntsReview.
\textbf{g)} Integration with De-Fi services like \emph{Dai} and \emph{Chai}, to be used as tokens in the protocol.
\textbf{h)} Library used by the protocol for secure contract development with the modules listed.}
\label{fig:contracts}
\end{figure}

@@

\subsubsection{AntsReview.}
AntsReview (see Figure \ref{fig:contracts}a) is the core of the smart contracts written in \emph{Solidity}\footnote[6]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine, deployed on Ethereum Rinkeby's Testnet\footnote[7]{\emph{Rinkeby Testnet}.\textsc{URL:}https://rinkeby.etherscan.io.}. AntsReview implements a bounty-like system where Alice (issuer) can issue an AntReview with the function \emph{issueAntReview()}.
\newline In order to create a transparent and openly accessible AntReview, Alice has to complete a series of required tasks:
 \newline 1. \emph{upload of the file} containing the requirements of the peer-review and the paper to be reviewed into IPFS and specification of the IPFS hash to be stored in the Ethereum blockchain as PoE;
 \newline 2. \emph{specification of a deadline} in the form of a unix timestamp after which the fulfillment will no longer be accepted;
 \newline 3. \emph{specification of the amount of Ether} for the reward that will be transferred from Alice to the contract.
 \newline Bob (peer-reviewer) downloads the file with Alice's paper and requirements by leveraging on the content-addressing feature of IPFS, that allows anyone to find the document using an IPFS explorer; subsequently, Bob can submit a peer-review before the deadline by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, by specifying the AntReview of interest as well as the IPFS Hash of the peer-review uploaded on IPFS.
Alice can accept the peer-review submitted by Bob with the function \emph{acceptAntReview()}, by specifying the AntReview as well as the peer-review of interest, that will transfer the reward specified for the AntReview from the contract to Bob.
If Alice does not receive any peer-review, she can cancel the AntReview with the function \emph{cancelAntReview()}, by specifying the AntReview of interest, and the contract will transfer the reward for the AntReview back to Alice.

Access management of the Ants-Review protocol is defined and controlled by AntsReviewRoles (See Figure \ref{fig:contracts} \textbf{b}). It's implemented by leveraging on \emph{AccessControl.sol} by OpenZeppelin Solidity Library\footnote[8]{\emph{OpenZeppelin Library}.\textsc{URL:}https://openzeppelin.com.}, through the creation of the Issuer and Peer-Reviewer Roles.
\newline It also integrates a circuit breaker design pattern via \emph{Pausable.sol} by OpenZeppelin to allow the Pauser Role, that by default is the Owner of the smart contracts, able to pause (or unpause) the functions in case of a security emergency, such as an attack to the smart contracts. In this way, only the Issuer can create a new AntReview.

\subsubsection{Tokenomics}
AntsReview integrates a few \emph{ERC20}\footnote[9]{\emph{EIP 20}.\textsc{URL:}\url{https://eips.ethereum.org/EIPS/eip-20}.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
\newline ANTS (see Figure \ref{fig:contracts}, c), is the primary protocol ERC20 token and can be staked into an AntReview.
\newline ANTS is implemented by inheriting \emph{ERC20PresetMinterPauser.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
\newline zkANTS (see Figure \ref{fig:contracts}, d), is a wrapper of ANTS that will be used inside the protocol to allow private transactions among the agents, preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters (members of Ants-Review Community).
\newline zkANTS will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens. In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token, that follows the EIP-1724 standard \footnote[10]{\emph{EIP  1724}.\textsc{URL:}\url{https://github.com/ethereum/EIPs/issues/1724.}} will be used as template to build an AZTEC-compatible asset.
\newline To optimize and scale transactions, AZTEC Protocol ZK-SNARKs, will be extended in the future to PLONK \cite{PLONK} to collapse the gas costs of private transactions.

>>>>

\begin{figure}
\centering
\includegraphics[scale=0.28]{AntsReview}
\caption{Exagones represent the protocol's smart contracts. Ellipse represents the smart contract inherited by AntsReview. Clouds represent integrations into the protocol. Rectangles represent smart contracts' libraries.
\textbf{a} Core contract of the protocol implementing a bounty system with the functions listed.
\textbf{b} Module inherited by AntsReview: it manages the access control of the protocol by adding and removing issuers and peer-reviewers.
\textbf{c} Native token used in the protocol that inherits the \textbf{d} contract from \emph{OpenZeppelin}. It is linked to (\textbf{a}) and to (\textbf{e}), wrapped into \emph{zkANTS} to implement private \emph{ANTS} transactions on Ethereum.
\textbf{f} Integration with IPFS to upload papers, requirements and peer-reviews and store the hash as \emph{PoE} into AntsReview.
\textbf{g} Integration with De-Fi services like \emph{Dai} and \emph{Chai}, to be used as tokens in the protocol.
\textbf{h} Library used by the protocol for secure contract development with the modules listed.}
\label{fig:contracts}
\end{figure}

@@

\subsubsection{AntsReview.}
AntsReview (see Figure \ref{fig:contracts} (\textbf{a}) is the core of the smart contracts written in \emph{Solidity}\footnote[6]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine, deployed on Ethereum Rinkeby's Testnet\footnote[7]{\emph{Rinkeby Testnet}.\textsc{URL:}https://rinkeby.etherscan.io.}. AntsReview implements a bounty-like system where Alice (issuer) can issue an AntReview with the function \emph{issueAntReview()}.
\newline In order to create a transparent and openly accessible AntReview, Alice has to complete a series of required tasks:
 \newline 1. \emph{upload of the file} containing the requirements of the peer-review and the paper to be reviewed into IPFS and specification of the IPFS hash to be stored in the Ethereum blockchain as PoE;
 \newline 2. \emph{specification of a deadline} in the form of a unix timestamp after which the fulfillment will no longer be accepted;
 \newline 3. \emph{specification of the amount of Ether} for the reward that will be transferred from Alice to the contract.
 \newline Bob (peer-reviewer) downloads the file with Alice's paper and requirements by leveraging on the content-addressing feature of IPFS, that allows anyone to find the document using an IPFS explorer; subsequently, Bob can submit a peer-review before the deadline by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, by specifying the AntReview of interest as well as the IPFS Hash of the peer-review uploaded on IPFS.
Alice can accept the peer-review submitted by Bob with the function \emph{acceptAntReview()}, by specifying the AntReview as well as the peer-review of interest, that will transfer the reward specified for the AntReview from the contract to Bob.
If Alice does not receive any peer-review, she can cancel the AntReview with the function \emph{cancelAntReview()}, by specifying the AntReview of interest, and the contract will transfer the reward for the AntReview back to Alice.

Access management of the Ants-Review protocol is defined and controlled by AntsReviewRoles (see Figure \ref{fig:contracts} (\textbf{b})). It is implemented by leveraging on \emph{AccessControl.sol} by OpenZeppelin Solidity Library\footnote[8]{\emph{OpenZeppelin Library}.\textsc{URL:}https://openzeppelin.com.}, through the creation of the Issuer and Peer-Reviewer Roles.
\newline It also integrates a circuit breaker design pattern via \emph{Pausable.sol} by OpenZeppelin to allow the Pauser Role, that by default is the Owner of the smart contracts, able to pause (or unpause) the functions in case of a security emergency, such as an attack to the smart contracts. In this way, only the Issuer can create a new AntReview.

\subsubsection{Tokenomics}
AntsReview integrates a few \emph{ERC20}\footnote[9]{\emph{EIP 20}.\textsc{URL:}\url{https://eips.ethereum.org/EIPS/eip-20}.} tokens, each of which plays an integral role in the functioning and anonymity of the decentralized protocol.
\newline ANTS (see Figure \ref{fig:contracts}, (\textbf{c})), is the primary protocol ERC20 token and can be staked into an AntReview.
\newline ANTS is implemented by inheriting \emph{ERC20PresetMinterPauser.sol} from OpenZeppelin Library with name \emph{Ants-Review} and symbol \emph{ANTS}.
\newline zkANTS (see Figure \ref{fig:contracts}, (\textbf{d})), is a wrapper of ANTS that will be used inside the protocol to allow private transactions among the agents, preserving their anonymity as well as the amount of the AntReview reward and the contributions by the Anters (members of Ants-Review Community).
\newline zkANTS will be implemented via AZTEC Protocol \cite{AZTEC}, that uses a cryptographic engine \emph{ACE.sol}, a contract responsible for validating the set of AZTEC zero-knowledge proofs and performing any transfer instructions involving AZTEC notes, minted into a zkAsset, that can be converted into ERC20 tokens. In order to implement a zkAsset called zkANTS, \emph{zkAsset.sol}, a contract implementation of a confidential token, that follows the EIP-1724 standard \footnote[10]{\emph{EIP  1724}.\textsc{URL:}\url{https://github.com/ethereum/EIPs/issues/1724.}} will be used as template to build an AZTEC-compatible asset.
\newline To optimize and scale transactions, AZTEC Protocol ZK-SNARKs, will be extended in the future to PLONK \cite{PLONK} to collapse the gas costs of private transactions.
